### 2024-05-08 thesis/sections/6.3-reference-resolution.tex
language analysis

        {1}                           & {2}     & \textcolor{purple}{34,91}           & \textcolor{purple}{34,81\%}         & \textcolor{purple}{40,61}                & \textcolor{purple}{25,48\%} & {39,13}                   & {25\%}                      \\
        {1}                           & {10}    & \textcolor{purple}{35,31}           & {40,15\%}                           & \textcolor{purple}{38,73}                & \textcolor{purple}{28,12\%} & \textcolor{purple}{44,19} & {20,53\%}                   \\
        {1}                           & {16}    & \textcolor{purple}{35,4}            & {42,93\%}                           & \textcolor{purple}{39,58}                & \textcolor{purple}{26,17\%} & {39,64}                   & {24,18\%}                   \\
        {1}                           & {50}    & {32,64}                             & {42,01\%}                           & \textcolor{purple}{38,99}                & \textcolor{purple}{28,52\%} & \textcolor{purple}{42,61} & {20,79\%}                   \\
        {1}                           & {100}   & \textcolor{purple}{36,73}           & \textcolor{purple}{31,21\%}         & \textcolor{purple}{40,25}                & \textcolor{purple}{24,91\%} & \textcolor{purple}{41,5}  & {21,44\%}                   \\
        {2}                           & {2}     & \textcolor{purple}{33,76}           & {40,67\%}                           & {35,86}                                  & {31,73\%}                   & \textcolor{purple}{41,79} & {22,14\%}                   \\
        {2}                           & {10}    & {31,37}                             & {43,27\%}                           & {37,23}                                  & \textcolor{purple}{30,34\%} & \textcolor{purple}{42,53} & \textcolor{purple}{19,75\%} \\
        {2}                           & {16}    & {31,19}                             & {46,27\%}                           & \textcolor{purple}{39,38}                & \textcolor{purple}{28,21\%} & \textcolor{purple}{41,74} & {22,7\%}                    \\
        {2}                           & {50}    & \textcolor{purple}{33,66}           & {39,28\%}                           & \textcolor{purple}{39,62}                & \textcolor{purple}{25,35\%} & \textcolor{purple}{45,63} & \textcolor{purple}{17,93\%} \\
        {2}                           & {100}   & \textcolor{purple}{35,1}            & \textcolor{purple}{34,81\%}         & \textcolor{purple}{39,86}                & \textcolor{purple}{27,3\%}  & \textcolor{purple}{45,45} & \textcolor{purple}{19,05\%} \\
        {3}                           & {2}     & {32,99}                             & {41,15\%}                           & {37,76}                                  & \textcolor{purple}{30,99\%} & \textcolor{purple}{46,45} & {20,92\%}                   \\
        {3}                           & {10}    & \textcolor{purple}{33,74}           & {38,89\%}                           & \textcolor{purple}{40,71}                & \textcolor{purple}{26,48\%} & \textcolor{purple}{44,53} & \textcolor{purple}{19,01\%} \\
        {3}                           & {16}    & \textcolor{purple}{34,18}           & {38,98\%}                           & \textcolor{purple}{38,52}                & \textcolor{purple}{30,03\%} & \textcolor{purple}{41,22} & {21,53\%}                   \\
        {3}                           & {50}    & \textcolor{purple}{34,38}           & {38,93\%}                           & \textcolor{purple}{39,52}                & \textcolor{purple}{26,74\%} & {38,4}                    & {24,87\%}                   \\
        {3}                           & {100}   & \textcolor{purple}{33,16}           & {40,19\%}                           & \textcolor{purple}{39,75}                & \textcolor{purple}{27,78\%} & \textcolor{purple}{41,29} & {21,83\%}                   \\
        {4}                           & {2}     & \textcolor{purple}{33,48}           & {40,36\%}                           & \textcolor{purple}{38,28}                & \textcolor{purple}{30,9\%}  & \textcolor{purple}{42,53} & {22,4\%}                    \\
        {4}                           & {10}    & \textcolor{purple}{35,01}           & {39,97\%}                           & \textcolor{purple}{40,88}                & \textcolor{purple}{26,39\%} & \textcolor{purple}{42,33} & {20,44\%}                   \\
        {4}                           & {16}    & \textcolor{purple}{35,59}           & \textcolor{purple}{35,59\%}         & \textcolor{purple}{37,91}                & {31,86\%}                   & \textcolor{purple}{41,9}  & {20,27\%}                   \\
        {4}                           & {50}    & \textcolor{purple}{34,99}           & {36,68\%}                           & \textcolor{purple}{40,89}                & \textcolor{purple}{23,26\%} & \textcolor{purple}{43,77} & \textcolor{purple}{18,36\%} \\
        {4}                           & {100}   & \textcolor{purple}{35,46}           & {37,46\%}                           & \textcolor{purple}{38,53}                & \textcolor{purple}{29,08\%} & {40,6}                    & {21,22\%}                   \\
        {6}                           & {2}     & \textcolor{purple}{34,97}           & {37,28\%}                           & \textcolor{purple}{39,52}                & \textcolor{purple}{29,69\%} & {40,53}                   & {24,7\%}                    \\
        {6}                           & {10}    & {32,39}                             & {43,53\%}                           & \textcolor{purple}{38,61}                & \textcolor{purple}{28,26\%} & {40,84}                   & {21,74\%}                   \\
        {6}                           & {16}    & \textcolor{purple}{34,87}           & \textcolor{purple}{34,38\%}         & \textcolor{purple}{39,03}                & \textcolor{purple}{26,82\%} & {40,34}                   & {23,31\%}                   \\
        {6}                           & {50}    & \textcolor{purple}{33,85}           & {37,07\%}                           & \textcolor{purple}{39,39}                & \textcolor{purple}{27,17\%} & {40,8}                    & {22,09\%}                   \\
        {6}                           & {100}   & \textcolor{purple}{34,62}           & {40,02\%}                           & \textcolor{purple}{39,46}                & \textcolor{purple}{25,48\%} & \textcolor{purple}{42,53} & \textcolor{purple}{18,4\%}  \\

@@

        {1}                           & {2}       & {93,3\%}                            & {65,36\%}                           & \textcolor{purple}{39,22\%}              \\
        {1}                           & {10}      & {93,85\%}                           & \textcolor{purple}{46,97\%}         & \textcolor{purple}{40,1\%}               \\
        {1}                           & {16}      & {92,06\%}                           & {76,68\%}                           & \textcolor{purple}{36,43\%}              \\
        {1}                           & {50}      & {94\%}                              & {76,43\%}                           & \textcolor{purple}{39,97\%}              \\
        {1}                           & {100}     & {94,03\%}                           & \textcolor{purple}{54,14\%}         & \textcolor{purple}{40,27\%}              \\
        {2}                           & {2}       & {92,27\%}                           & \textcolor{purple}{52,15\%}         & \textcolor{purple}{33,64\%}              \\
        {2}                           & {10}      & \textbf{96,16\%}                    & {80,26\%}                           & \textcolor{purple}{36,53\%}              \\
        {2}                           & {16}      & {95,84\%}                           & \textbf{84,03\%}                    & \textcolor{purple}{39,65\%}              \\
        {2}                           & {50}      & {93,78\%}                           & \textcolor{purple}{52,24\%}         & \textcolor{purple}{39,56\%}              \\
        {2}                           & {100}     & {92,43\%}                           & \textcolor{purple}{53,23\%}         & \textcolor{purple}{37,68\%}              \\
        {3}                           & {2}       & {94,52\%}                           & \textcolor{purple}{51,97\%}         & \textcolor{purple}{37,09\%}              \\
        {3}                           & {10}      & {94,9\%}                            & \textcolor{purple}{53,47\%}         & \textcolor{purple}{38,24\%}              \\

@@

        {3}                           & {50}      & {93,88\%}                           & {79,65\%}                           & \textcolor{purple}{40,36\%}              \\
        {3}                           & {100}     & {95,25\%}                           & \textcolor{purple}{48,52\%}         & \textcolor{purple}{42,55\%}              \\
        {4}                           & {2}       & {89,15\%}                           & \textcolor{purple}{51,98\%}         & \textcolor{purple}{39,68\%}              \\
        {4}                           & {10}      & \textbf{96,08\%}                    & \textcolor{purple}{48,03\%}         & \textbf{64,31\%}                         \\
        {4}                           & {16}      & {94,14\%}                           & \textcolor{purple}{49,81\%}         & \textcolor{purple}{40,84\%}              \\
        {4}                           & {50}      & \textbf{96,24\%}                    & \textcolor{purple}{48,79\%}         & \textcolor{purple}{43,61\%}              \\
        {4}                           & {100}     & {95,55\%}                           & \textcolor{purple}{49,65\%}         & \textcolor{purple}{42,85\%}              \\
        {6}                           & {2}       & \textcolor{purple}{59,68\%}         & \textcolor{purple}{53,57\%}         & \textcolor{purple}{38,43\%}              \\
        {6}                           & {10}      & \textcolor{purple}{63,46\%}         & \textbf{82,12\%}                    & \textcolor{purple}{40,11\%}              \\
        {6}                           & {16}      & {95,86\%}                           & \textcolor{purple}{50,71\%}         & \textcolor{purple}{40,61\%}              \\
        {6}                           & {50}      & {91,27\%}                           & \textcolor{purple}{52,55\%}         & \textcolor{purple}{40,21\%}              \\
        {6}                           & {100}     & \textcolor{purple}{60,27\%}         & \textcolor{purple}{46,92\%}         & \textcolor{purple}{41,98\%}              \\

>>>>

        {1}                           & {2}     & \textcolor{red}{34,91}              & \textcolor{red}{34,81\%}            & \textcolor{red}{40,61}                   & \textcolor{red}{25,48\%} & {39,13}                & {25\%}                   \\
        {1}                           & {10}    & \textcolor{red}{35,31}              & {40,15\%}                           & \textcolor{red}{38,73}                   & \textcolor{red}{28,12\%} & \textcolor{red}{44,19} & {20,53\%}                \\
        {1}                           & {16}    & \textcolor{red}{35,4}               & {42,93\%}                           & \textcolor{red}{39,58}                   & \textcolor{red}{26,17\%} & {39,64}                & {24,18\%}                \\
        {1}                           & {50}    & {32,64}                             & {42,01\%}                           & \textcolor{red}{38,99}                   & \textcolor{red}{28,52\%} & \textcolor{red}{42,61} & {20,79\%}                \\
        {1}                           & {100}   & \textcolor{red}{36,73}              & \textcolor{red}{31,21\%}            & \textcolor{red}{40,25}                   & \textcolor{red}{24,91\%} & \textcolor{red}{41,5}  & {21,44\%}                \\
        {2}                           & {2}     & \textcolor{red}{33,76}              & {40,67\%}                           & {35,86}                                  & {31,73\%}                & \textcolor{red}{41,79} & {22,14\%}                \\
        {2}                           & {10}    & {31,37}                             & {43,27\%}                           & {37,23}                                  & \textcolor{red}{30,34\%} & \textcolor{red}{42,53} & \textcolor{red}{19,75\%} \\
        {2}                           & {16}    & {31,19}                             & {46,27\%}                           & \textcolor{red}{39,38}                   & \textcolor{red}{28,21\%} & \textcolor{red}{41,74} & {22,7\%}                 \\
        {2}                           & {50}    & \textcolor{red}{33,66}              & {39,28\%}                           & \textcolor{red}{39,62}                   & \textcolor{red}{25,35\%} & \textcolor{red}{45,63} & \textcolor{red}{17,93\%} \\
        {2}                           & {100}   & \textcolor{red}{35,1}               & \textcolor{red}{34,81\%}            & \textcolor{red}{39,86}                   & \textcolor{red}{27,3\%}  & \textcolor{red}{45,45} & \textcolor{red}{19,05\%} \\
        {3}                           & {2}     & {32,99}                             & {41,15\%}                           & {37,76}                                  & \textcolor{red}{30,99\%} & \textcolor{red}{46,45} & {20,92\%}                \\
        {3}                           & {10}    & \textcolor{red}{33,74}              & {38,89\%}                           & \textcolor{red}{40,71}                   & \textcolor{red}{26,48\%} & \textcolor{red}{44,53} & \textcolor{red}{19,01\%} \\
        {3}                           & {16}    & \textcolor{red}{34,18}              & {38,98\%}                           & \textcolor{red}{38,52}                   & \textcolor{red}{30,03\%} & \textcolor{red}{41,22} & {21,53\%}                \\
        {3}                           & {50}    & \textcolor{red}{34,38}              & {38,93\%}                           & \textcolor{red}{39,52}                   & \textcolor{red}{26,74\%} & {38,4}                 & {24,87\%}                \\
        {3}                           & {100}   & \textcolor{red}{33,16}              & {40,19\%}                           & \textcolor{red}{39,75}                   & \textcolor{red}{27,78\%} & \textcolor{red}{41,29} & {21,83\%}                \\
        {4}                           & {2}     & \textcolor{red}{33,48}              & {40,36\%}                           & \textcolor{red}{38,28}                   & \textcolor{red}{30,9\%}  & \textcolor{red}{42,53} & {22,4\%}                 \\
        {4}                           & {10}    & \textcolor{red}{35,01}              & {39,97\%}                           & \textcolor{red}{40,88}                   & \textcolor{red}{26,39\%} & \textcolor{red}{42,33} & {20,44\%}                \\
        {4}                           & {16}    & \textcolor{red}{35,59}              & \textcolor{red}{35,59\%}            & \textcolor{red}{37,91}                   & {31,86\%}                & \textcolor{red}{41,9}  & {20,27\%}                \\
        {4}                           & {50}    & \textcolor{red}{34,99}              & {36,68\%}                           & \textcolor{red}{40,89}                   & \textcolor{red}{23,26\%} & \textcolor{red}{43,77} & \textcolor{red}{18,36\%} \\
        {4}                           & {100}   & \textcolor{red}{35,46}              & {37,46\%}                           & \textcolor{red}{38,53}                   & \textcolor{red}{29,08\%} & {40,6}                 & {21,22\%}                \\
        {6}                           & {2}     & \textcolor{red}{34,97}              & {37,28\%}                           & \textcolor{red}{39,52}                   & \textcolor{red}{29,69\%} & {40,53}                & {24,7\%}                 \\
        {6}                           & {10}    & {32,39}                             & {43,53\%}                           & \textcolor{red}{38,61}                   & \textcolor{red}{28,26\%} & {40,84}                & {21,74\%}                \\
        {6}                           & {16}    & \textcolor{red}{34,87}              & \textcolor{red}{34,38\%}            & \textcolor{red}{39,03}                   & \textcolor{red}{26,82\%} & {40,34}                & {23,31\%}                \\
        {6}                           & {50}    & \textcolor{red}{33,85}              & {37,07\%}                           & \textcolor{red}{39,39}                   & \textcolor{red}{27,17\%} & {40,8}                 & {22,09\%}                \\
        {6}                           & {100}   & \textcolor{red}{34,62}              & {40,02\%}                           & \textcolor{red}{39,46}                   & \textcolor{red}{25,48\%} & \textcolor{red}{42,53} & \textcolor{red}{18,4\%}  \\

@@

        {1}                           & {2}       & {93,3\%}                            & {65,36\%}                           & \textcolor{red}{39,22\%}                 \\
        {1}                           & {10}      & {93,85\%}                           & \textcolor{red}{46,97\%}            & \textcolor{red}{40,1\%}                  \\
        {1}                           & {16}      & {92,06\%}                           & {76,68\%}                           & \textcolor{red}{36,43\%}                 \\
        {1}                           & {50}      & {94\%}                              & {76,43\%}                           & \textcolor{red}{39,97\%}                 \\
        {1}                           & {100}     & {94,03\%}                           & \textcolor{red}{54,14\%}            & \textcolor{red}{40,27\%}                 \\
        {2}                           & {2}       & {92,27\%}                           & \textcolor{red}{52,15\%}            & \textcolor{red}{33,64\%}                 \\
        {2}                           & {10}      & \textbf{96,16\%}                    & {80,26\%}                           & \textcolor{red}{36,53\%}                 \\
        {2}                           & {16}      & {95,84\%}                           & \textbf{84,03\%}                    & \textcolor{red}{39,65\%}                 \\
        {2}                           & {50}      & {93,78\%}                           & \textcolor{red}{52,24\%}            & \textcolor{red}{39,56\%}                 \\
        {2}                           & {100}     & {92,43\%}                           & \textcolor{red}{53,23\%}            & \textcolor{red}{37,68\%}                 \\
        {3}                           & {2}       & {94,52\%}                           & \textcolor{red}{51,97\%}            & \textcolor{red}{37,09\%}                 \\
        {3}                           & {10}      & {94,9\%}                            & \textcolor{red}{53,47\%}            & \textcolor{red}{38,24\%}                 \\

@@

        {3}                           & {50}      & {93,88\%}                           & {79,65\%}                           & \textcolor{red}{40,36\%}                 \\
        {3}                           & {100}     & {95,25\%}                           & \textcolor{red}{48,52\%}            & \textcolor{red}{42,55\%}                 \\
        {4}                           & {2}       & {89,15\%}                           & \textcolor{red}{51,98\%}            & \textcolor{red}{39,68\%}                 \\
        {4}                           & {10}      & \textbf{96,08\%}                    & \textcolor{red}{48,03\%}            & \textbf{64,31\%}                         \\
        {4}                           & {16}      & {94,14\%}                           & \textcolor{red}{49,81\%}            & \textcolor{red}{40,84\%}                 \\
        {4}                           & {50}      & \textbf{96,24\%}                    & \textcolor{red}{48,79\%}            & \textcolor{red}{43,61\%}                 \\
        {4}                           & {100}     & {95,55\%}                           & \textcolor{red}{49,65\%}            & \textcolor{red}{42,85\%}                 \\
        {6}                           & {2}       & \textcolor{red}{59,68\%}            & \textcolor{red}{53,57\%}            & \textcolor{red}{38,43\%}                 \\
        {6}                           & {10}      & \textcolor{red}{63,46\%}            & \textbf{82,12\%}                    & \textcolor{red}{40,11\%}                 \\
        {6}                           & {16}      & {95,86\%}                           & \textcolor{red}{50,71\%}            & \textcolor{red}{40,61\%}                 \\
        {6}                           & {50}      & {91,27\%}                           & \textcolor{red}{52,55\%}            & \textcolor{red}{40,21\%}                 \\
        {6}                           & {100}     & \textcolor{red}{60,27\%}            & \textcolor{red}{46,92\%}            & \textcolor{red}{41,98\%}                 \\

### 2024-05-08 thesis/sections/7-language-analysis.tex
language analysis

\section{Analysis of the emerged languages}
\label{sec:analysis_language}
The languages that emerge are analyzed in two ways.
First, for each language that emerges through successful communication, a score is calculated that represents the similarity of the messages to valid English referring expressions.
In a second step, several languages are analyzed qualitatively, to determine what certain symbols mean and what they might refer to in the visual scenes.
\cmtDK[inline]{talks about why and which few languages}

@@

Tables \ref{tab:probing:re-generator:dale-2} and \ref{tab:probing:re-generator:dale-5} show the results of the probing on the emerged languages of the \emph{referring expression generation games}.
This is the only task, where the final task for the agents is to generate English referring expressions with the salience order 'Sh > C > Si'.
English referring expressions are therefore explicitly passed to the agents as correct labels during training.
One can therefore expect the agents to align their own language with the target referring expressions and a high correlation with the salience order 'Sh > C > Si' is expected.
Looking at the results, this is partially confirmed for the 'Dale-2' dataset.
Some emerged languages reach with a normalized loss of 49,22\% one of the highest correlations to English referring expressions across all emerged languages in this thesis.
However, the salience order with the highest correlation is 'Sh > Si > C', and values the \emph{size} more than the \emph{color}, instead of the reversed way as in the training data of the agents.
The color seems, as in the previous task, not as important to communicate as the other attributes.
While the \emph{size} plays a bigger role, the \emph{shape} is the central attribute in the communication.
This fact is interesting for two reasons:
First, the \emph{shape} being the most important attribute in the messages aligns with the receiver's generated referring expressions where the \emph{shape} was predicted almost perfectly.
The receiver therefore seems to make use of the sender's ability to extract the \emph{shape} from the images and reproduces what the sender communicated.
However, without a deeper analysis, it can't be ruled out that the receiver extracts the \emph{shape} themselves from the image, and uses the sender's message only to determine the correct target object in the scene.
Secondly, this does not apply to the \emph{size} and the \emph{color}.
While the size seems to be communicated, it is not generated correctly by the receiver.
The opposite applies to the \emph{color}.
The \emph{color} is not important in the communication, but the receiver however is able to produce correct colors in the generated referring expression.
This shows that the agents actually don't align their own language with the target referring expression.
The communication of the target object between the agents seems to be a separate step from the receiver's generation of the referring expression.

@@

On the 'Dale-5' dataset, the emerged languages again resemble the English referring expressions less.
While the dominant salience order is 'Sh > Si > C' as on the 'Dale-2' dataset, the \emph{color} plays a bigger role.
This effect is the same as for the discrimination games, and can be explained by the higher number or distractors.
While the loss for the salience order 'Sh > Si > C' is lower than 70\% for two languages, it stays between 70\% and 80\% for most.

>>>>

\section{Analysis of the emerged languages}
\label{sec:analysis_language}
The languages that emerge are analyzed in two ways.
First, for each language that emerges through successful communication, a score is calculated that represents the similarity of the messages to valid English referring expressions.
In a second step, several languages are analyzed qualitatively, to determine what certain symbols mean and what they might refer to in the visual scenes.
\cmtDK[inline]{talks about why and which few languages}
\cmtDK[inline]{chosen salience order might be due to number of possibilities (more efficient to exclude larger number of distractors instantly)}

@@

Tables \ref{tab:probing:re-generator:dale-2} and \ref{tab:probing:re-generator:dale-5} show the results of the probing on the emerged languages of the \emph{referring expression generation games}.
This is the only task, where the final task for the agents is to generate English referring expressions with the salience order 'Sh > C > Si'.
English referring expressions are therefore explicitly passed to the agents as correct labels during training.
One can therefore expect the agents to align their own language with the target referring expressions and a high correlation with the salience order 'Sh > C > Si' is expected.
Looking at the results, this is partially confirmed for the 'Dale-2' dataset.
Some emerged languages reach with a normalized loss of 49,22\% one of the highest correlations to English referring expressions across all emerged languages in this thesis.
However, the salience order with the highest correlation is 'Sh > Si > C', and values the \emph{size} more than the \emph{color}, instead of the reversed way as in the training data of the agents.
The color seems, as in the previous task, not as important to communicate as the other attributes.
While the \emph{size} plays a bigger role, the \emph{shape} is the central attribute in the communication.
This fact is interesting for two reasons:
First, the \emph{shape} being the most important attribute in the messages aligns with the receiver's generated referring expressions where the \emph{shape} was predicted almost perfectly.
The receiver therefore seems to make use of the sender's ability to extract the \emph{shape} from the images and reproduces what the sender communicated.
However, without a deeper analysis, it can't be ruled out that the receiver extracts the \emph{shape} themselves from the image, and uses the sender's message only to determine the correct target object in the scene.
Secondly, this does not apply directly to the \emph{size} and the \emph{color}.
The \emph{size} seems to be communicated often by the sender to discriminate the target object.
On the other hand, as the target referring expression uses the salience order 'Sh > C > Si', the shape is only needed to be generated in $\frac{1}{3} * \frac{1}{8} \approx 4,2\%$ of the samples.
The opposite applies to the \emph{color}.
The \emph{color} is not important in the agents' communication, but the receiver however needs to produce colors in the generated referring expression in $\frac{1}{3} \approx 33,3\%$ of the samples.
This shows that the agents actually don't align their own language with the target referring expression.
The communication of the target object between the agents seems to be a separate step from the receiver's generation of the referring expression.

@@

On the 'Dale-5' dataset, the emerged languages again resemble the English referring expressions less.
While the dominant salience order is 'Sh > Si > C' as on the 'Dale-2' dataset, the \emph{color} plays a bigger role.
This effect is the same as for the discrimination games, and can be explained by the higher number of distractors.
While the loss for the salience order 'Sh > Si > C' is lower than 70\% for two languages, it stays between 70\% and 80\% for most.
Interesting now is that all attributes are communicated by the sender, while the receiver is also generating the correct attributes in the referring expression.
Opposed to the 'Dale-2' dataset, the need for \emph{size} and \emph{color} is much bigger to discriminate the target object in any salience order, due to the larger number of distractors.

$Lang_{6,50}$ is the emerged language, with which the agents can achieve the best results on the task.
While the receiver achieves high precision and recall scores on each attribute (recall Tables \ref{tab:results:re-generator-game_size-shape} and \ref{tab:results:re-generator-game_color}), each attribute also plays a bigger role in the message be the sender.
Indeed, one can see a correlation between the predictions of the receiver and the usage of attributes in emerged language.
A more frequent usage of an attribute in the emerged language leads to a more accurate generation of this attribute in the final referring expression.
